%!TEX TS-program = xelatex
\documentclass[]{patyoon-cv}
\addbibresource{bibliography.bib}

\begin{document}
\header{patrick}{yoon}
       {software engineer}


% In the aside, each new line forces a line break
\begin{aside}
  \section{about}
    18 Norfolk Street
    San Francisco, CA, 94103
    ~
    \href{mailto:me@patyoon.com}{me@patyoon.com}
    \href{http://patyoon.com}{http://patyoon.com}
    \href{http://twitter.com/patryoon}{twitter://patryoon}
    \href{http://github.com/patyoon}{github://patyoon}
  \section{languages}
    bilingual Korean/English
  \section{skills}
    JavaScript
    (jQuery, node.js),
    Python, C,
    Haskell, Git, SVN,
    CSS3 \& HTML5
\end{aside}

\section{education}

\begin{entrylist}
  \entry
    {2012–2013}
    {University of Pennsylvania}
    {Philadelphia PA, USA}
    {\begin{itemize}
      \item M.S.E. in Computer Science
      \item Graduated with master's thesis
      \end{itemize}
    }
  \entry
    {2008–2012}
    {University of Pennsylvania} 
    {Philadelphia PA, USA}
    {\begin{itemize}
      \item B.S.E. in Computer Science, magna cum laude
      \item Eta Kappa Ku, Vice President; Delta Tau Delta
    \end{itemize}}
  \entry
    {2005–2008}
    {Korea Science Academy} 
    {Busan }
    {\begin{itemize}
      \item High School
    \end{itemize}}
\end{entrylist}

\section{experience}

\begin{entrylist}
  \entry
      {08 2013-}
      {\href{http://tellapart.com/}{TellApart Inc.}}
      {Software Engineer}
      {\begin{itemize}
        \item Software Engineer starting in August 2013.  
        \end{itemize}
      } 
  \entry
      {Spring 13'}
      {\href{http://www.cis.upenn.edu/}{University of Pennsylvania}}
      {CIS 505 Teaching Assistant}
      {\begin{itemize}
        \item Taught graduate-level introduction to distributed systems course.
      \end{itemize}
      } 
  \entry
      {05–08 12'}
      {\href{http://bing.com/}{Microsoft Bing}}
      {Software Development Engineering Intern}
      {\begin{itemize}
        \item Built a classifier for deciding query intent in Bing Local Search Team that outperforms the existing classifier by 8.5\% in precision and recall on a sample query set.
        \item Experimented with ways of mining training data and semi-supervised approaches to label them and compared end-to-end metrics. 
        \end{itemize}} 
  \entry
    {03–10 12'}
    {\href{http://emeraldexam.com}{Emerald Exam (formerly Essaysafe)}}
    {Co-founder}
    {\begin{itemize}
      \item Developed a secure in-class testing application that allows students to take in-class exams using their laptops on Chrome Browser and allows professors to grade and give feedbacks to exams saved in cloud storage.
      \item Developed native Windows and OS X applications that prevents and reports cheating activities to the professor.
      \item Selected as top 20 teams in AngelHack Boston in March 2012.
      \end{itemize}} 
  \entry
    {Spring 12'}
    {\href{http://www.cis.upenn.edu/}{University of Pennsylvania}}
    {CIS 391/521 Teaching Assistant}
    {\begin{itemize}
        \item Taught upperclassmen/graduate-level intro to Artificial Intelligence course.
        \item Ran two make up lectures and Wrote four out of ten weekly assignments. 
        \item Set up and managed the server for class final project running \href{http://aichallenge.org/}{Ants AI Challenge}.
    \end{itemize}} 
  \entry
    {06–09 11'}
    {\href{http://www.google.com}{Google Inc.}}
    {Software Engineering Intern}
    {\begin{itemize}
      \item Developed a internal framework that periodically updates visualization for various statistics for AdWords advertisement formats.
      \item Implemented a new Search Ads format in Media Ads team and plugged into Google Web Server.
      \end{itemize}} 
  \entry
      {Fall 11'}
      {\href{http://www.cis.upenn.edu/}{University of Pennsylvania}}
      {CIS 121 Teaching Assistant}
      {\begin{itemize}
        \item Taught freshmen/sophomore-level data structures course in Java.
        \item Responsibility included weekly recitations, writing and grading assignments and exams.
      \end{itemize}} 
\end{entrylist}

\begin{entrylist}
    \entry
      {05 10' - 05 11'}
      {\href{http://www.ldc.upenn.edu/}{Lingustic Data Consortium}}
      {Student Programmer}
      {\begin{itemize}
        \item Improved GUI test tools for machine reading project.
        \item Developed web version of standalone tool for annotation of English corpora. 
        \item Processed Korean newswire data and published corpus. Greatly improved validity by fixing word segmentation issue. 
      \end{itemize}} 
  \entry
      {04-07 09'}
      {\href{http://www.lrsm.upenn.edu/}{The Laboratory for Research on the Structure of Matter}}
      {Research Assistant}
      {\begin{itemize}
        \item Participated in research on reconstruction of Breast Cancer Optical data and MRI image data.
        \item Built a C++ library from existing Perl codes that process various types of image data.
    \end{itemize}}   
\end{entrylist}
      
\section{projects}

\begin{entrylist}
  \entry
    {2011}
    {DJ Feed}
    {\href{http://djfeed.com}{djfeed.com}}
    {\begin{itemize}
      \item Developed an Android application that allows users to request or vote on upcoming songs to influence the playlist at a party. Developed with a team of two people. Users can rate the now playing song to give feedback to DJ, or check the playlist and ratings at other venues.
      \item DJ's can manage the playlist and view users' votes and feedback on desktop application.
      \item Won “Biggest Potential award,” for application that shows greatest business potential out of 30 total teams. 
      \end{itemize}
    }
  \entry
    {2011}
    {Bang Search Engine}
    {\href{http://patyoon.com/bang}{patyoon.com/bang}}
    {
      \begin{itemize}
      \item Developed a distributed, scalable web crawler for a peer-to-peer implementation of a search engine with indexing and ranking with team of four people. 
      \item Analyzed performance varying number of nodes and threads running on a node. 
      \end{itemize}
      }
\end{entrylist}

\section{research}
\begin{entrylist}
  \entry
    {2013}
    {Compositionality of English phrases}
    {Master's Thesis   \href{http://www.patyoon.com/master\_thesis\_final.pdf}{Final Deliverable}}
    {
      \begin{itemize}
      \item Studied approaches to mine sentiment data from research paper citations in order to determine the opinion toward the cited papers.
      \item Suggested methods and metrics to make observations about how research papers relate to one another using sentiments toward their content and role in citing papers.
      \item Generated regression models to make predictions about he future success of a paper based on the current sentiment toward the paper.
      \end{itemize}
    }
  \entry
    {2012}
    {Sentiment Analysis of Citations for Research Papers}
    {Undergraduate Senior Design Project  \href{http://www.patyoon.com/senior\_design\_final\_report.pdf}{Final Report}}
    {
      \begin{itemize}
      \item Studied approaches to mine sentiment data from research paper citations in order to determine the opinion toward the cited papers.
      \item Suggested methods and metrics to make observations about how research papers relate to one another using sentiments toward their content and role in citing papers.
      \item Generated regression models to make predictions about he future success of a paper based on the current sentiment toward the paper.
      \end{itemize}
    }    
\end{entrylist}
      
%% \section{publications}

%% \printbibsection{article}{article in peer-reviewed journal}
%% \begin{refsection}
%%   \nocite{*}
%%   \printbibliography[sorting=chronological, type=inproceedings, title={international peer-reviewed conferences/proceedings}, notkeyword={france}, heading=subbibliography]
%% \end{refsection}
%% \begin{refsection}
%%   \nocite{*}
%%   \printbibliography[sorting=chronological, type=inproceedings, title={local peer-reviewed conferences/proceedings}, keyword={france}, heading=subbibliography]
%% \end{refsection}
%% \printbibsection{misc}{other publications}
%% \printbibsection{report}{research reports}

\section{awards}

\begin{entrylist}
  \entry
      {2012}
      {\href{http://www.limeconnect.com/opportunities/page/google-lime-scholarship-program}
        {Google Lime Scholarship for Students with Disabilities}}
      { }
      {
        \begin{itemize}
        \item \$10,000 awarded based on the strength of candidates' academic background and demonstrated passion for computer science.
        \item Awarded to 14 students.
        \end{itemize}}
   \entry
       {2008}
       {Korea Presidential Science Scholarship}
       { }
       {
         \begin{itemize}
         \item Full tuition scholarship for 4 years awarded based on the strength of candidates' academic background and research experiences.
         \item Awarded to ten students annually.
         \end{itemize}
       }
\end{entrylist}

\end{document}
